---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# PesticideLoadIndex4Dummies

<!-- badges: start -->
<!-- badges: end -->

The goal of PesticideLoadIndex4Dummies is to generalize the calculations used in the Danish Pesticide Load Index and make them accessible for anyone to use. Particuarly the folks in the ADOPT-IPM consortium. 

## Installation

You can install the development version of PesticideLoadIndex4Dummies from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("vanichols/PesticideLoadIndex4Dummies")
```

## Example

Right now the GetLoadIndex just scales the value to be between 0 and 1, where 0 represents 
the most benign substance in the database, and 1 represents the most toxic. The scale is logarithmic.

```{r example}
library(PesticideLoadIndex4Dummies)
#GetLoadIndex(f_dat = pli_examdat)
```
